An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
Comments on top k

\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$}
\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\U$.
  The \emph{level set} of $\Gamma$ for report $u$ is the set $\Gamma_u := \{p : u \in \Gamma(p)\}$.
\end{definition}

@@

We write the surrogate $L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.

@@

	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
	Consider
	\begin{align*}
		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
%		&\leq \frac{k+1}{2k} \\
%		&\leq 1
	\end{align*}
	\jessie{TODO-- Not sure how.  Two thoughts: can we leverage Jensen's inequality since we have convexity?  Or can we show these are supporting hyperplanes of the risk?  Another question-- is the risk polyhedral?}

>>>>

\bo{The following is not ideal because everywhere else in the paper, we always use $\R$ with $\gamma$ and $\reals^d$ with $\Gamma$} \jessie{Is this better?}
\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\U$.
  The \emph{level set} of $\Gamma$ for report $u$ is the set $\Gamma_u := \{p : u \in \Gamma(p)\}$.
\end{definition}

@@

We write the surrogate $L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right)_+ $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.
$L_2$ is a polyhedral loss, since it can be written as the pointwise max of $\binom{n}{k} +1$ terms, where the $\binom{n}{k}$ terms are selecting the $k$ elements of $u + \indopp(y)$ with highest weight.
By Lemma~\ref{lem:poly-loss-poly-risk}, we then know that $\risk{L_2}$ is also polyhedral.

@@

	For the first case, we claim that $e_y \in \argmin_{u \in [0,1]^n} \inprod{p}{L_2(u)}$.
	Consider
	\begin{align*}
		L_2(e_y, p) &= \sum_{y' \neq y} p_{y'} L_2(e_y, y') + L_2(e_y, y)\\
		&= \frac{k+1}{k} (1 - p_y) %+ 0 \\
%		&\leq \frac{k+1}{2k} \\
%		&\leq 1
	\end{align*}
	\jessie{TODO-- Not sure how.  Two thoughts: can we leverage Jensen's inequality since we have convexity?  Or can we show these are supporting hyperplanes of the risk?}
